News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-09-05 rupnik2015.tex
overview fixed

The paper is organized as follows: we first provide an overview of the system as a whole (Section~\ref{sec:pipeline}), which includes a subsection that summarizes the main system requirements in Section~\ref{sec:sysreq}. We then present related work in Section~\ref{sec:related}. The related work covers work on cross-lingual document similarity as well as work on cross-lingual cluster linking. In Section~\ref{sec:crosslingual} we introduce the main problem of cross-lingual document similarity computation, which is followed by an overview of the models that we considered in Section~\ref{sec:models}. We then establish necessary notation in Section~\ref{sec:notation} and proceed with four subsections that describe the main cross-lingual similarity approaches in detail. The approach in Section~\ref{sec:kmeans} serves as a baseline, and the approaches in Section~\ref{sec:CCA} and Section~\ref{sec:LSI} serve as the basis on which we proposed a new approach presented in Section~\ref{sec:hublang}. In Section~\ref{sec:linking} we introduce the central problem of cross-lingual linking of clusters of news articles and our approach that combines the cross-lingual similarity functions with knowledge extraction based techniques. Finally, we present and interpret the experimental results in Section~\ref{sec:evaluation} and discuss conclusions and point out several promising future directions.

@@

As a next step, an online clustering algorithm is applied to the articles in order to identify groups of articles that are discussing the same event. For each new article, the clustering algorithm determines if the article should be assigned to some existing cluster or into a new cluster. The underlying assumption is that articles that are describing the same event are similar enough and will therefore be put into the same cluster. For clustering, each new article is first tokenized, stop words are removed and the remaining words are stemmed.
The remaining tokens are represented in a vector-space model and normalized using TF-IDF\footnote{The IDF weights are dynamically computed for each new article over all news articles within a 10 day window.} (see Section~\ref{sec:tfidf} for the definition). Cosine similarity is used to find the most similar existing cluster, by comparing the document's vector to the centroid vector of each cluster. A user-defined threshold is used to determine if the article is not similar enough to any existing clusters (0.4 was used in our experiments).  If the highest similarity is above the threshold, the article is assigned to the corresponding cluster, otherwise a new cluster is created, initially containing only the single article. Whenever an article is assigned to a cluster, the cluster's centroid vector is also updated. Since articles about an event are commonly written only for a short period of time, we remove clusters once the oldest article in the cluster becomes more than 4 days old. This housekeeping mechanism prevents the clustering from becoming slow and also ensures that articles are not assigned to obsolete clusters. Details of the clustering approach are described in~\cite{brank2014}.

@@

\section{Related work}

>>>>

The paper is organized as follows: we first provide an overview of the system as a whole (Section~\ref{sec:pipeline}), which includes a subsection that summarizes the main system requirements. We then present related work in Section~\ref{sec:related}. The related work covers work on cross-lingual document similarity as well as work on cross-lingual cluster linking. In Section~\ref{sec:crosslingual}, we introduce the problem of cross-lingual document similarity computation, followed by an overview  and description of the main cross-lingual similarity approaches we consider in detail, including a new approach based on hub languages. 
%The approach in Section~\ref{sec:kmeans} serves as a baseline, and the approaches in Section~\ref{sec:CCA} and Section~\ref{sec:LSI} serve as the basis on which we proposed a new approach presented in Section~\ref{sec:hublang}
 In Section~\ref{sec:linking}, we introduce the central problem of cross-lingual linking of clusters of news articles and our approach that combines the cross-lingual similarity functions with knowledge extraction based techniques. Finally, we present and interpret the experimental results in Section~\ref{sec:evaluation} and discuss conclusions and point out several promising future directions.

@@

As the next step, an online clustering algorithm is applied to the articles in order to identify groups of articles that are discussing the same event. For each new article, the clustering algorithm determines if the article should be assigned to some existing cluster or into a new cluster. The underlying assumption is that articles that are describing the same event are similar enough and will therefore be put into the same cluster. For clustering, each new article is first tokenized, stop words are removed and the remaining words are stemmed.
The remaining tokens are represented in a vector-space model and normalized using TF-IDF\footnote{The IDF weights are dynamically computed for each new article over all news articles within a 10 day window.} (see Section~\ref{sec:tfidf} for the definition). Cosine similarity is used to find the most similar existing cluster, by comparing the document's vector to the centroid vector of each cluster. A user-defined threshold is used to determine if the article is not similar enough to any existing clusters (0.4 was used in our experiments).  If the highest similarity is above the threshold, the article is assigned to the corresponding cluster, otherwise a new cluster is created, initially containing only the single article. Whenever an article is assigned to a cluster, the cluster's centroid vector is also updated. Since articles about an event are commonly written only for a short period of time, we remove clusters once the oldest article in the cluster becomes more than 4 days old. This housekeeping mechanism prevents the clustering from becoming slow and also ensures that articles are not assigned to obsolete clusters. Details of the clustering approach are described in~\cite{brank2014}.

@@

\section{Related work}\label{sec:related}
